Experiment 3: ratings

### 2021-06-04 analysis/exp3_analysis.Rmd
exp 3 analysis

---
title: 'Experiment 3: ratings'
author: "George"
date: "6/3/2021"
output: html_document
---

@@

```{r cars}
library(png)
library(grid)
library(ggplot2)
library(xtable)
require(here)
require(tidyverse)
require(tidyboot)
library(apa) # for generating APA-style text to report statistical tests
library(ggpubr)
require(gridExtra)
require(papaja)
require(kableExtra)
require(qualtRics)
```

@@

sum(is.na(int_long$rating))
sum(is.na(lik_long$rating))
```

@@

```{r}
adult_agg <- adult_long %>% group_by(drop, target, relation) %>%
  summarize(chose_target = mean(chose_target)) # do we want raw counts for chose target vs. foil?
# for trial 1, 70% chose target (30% chose distractor)

child_agg <- child_long %>% group_by(drop, target, relation) %>%
  summarize(chose_target = mean(chose_target))
```

@@

```{r}
lik_agg <- lik_long %>% mutate(rating = as.numeric(rating)) %>%
  group_by(drop, choice) %>%
  summarise(likelihood = mean(rating))

int_agg <- lik_long %>% mutate(rating = as.numeric(rating)) %>%
  group_by(drop, choice) %>%
  summarise(interest = mean(rating)) 
# also want ratings scaled 0-1?
```

>>>>

---
title: 'Experiment 3: ratings'
author: "George, Sama, and Mike"
date: "6/3/2021"
output: html_document
---

@@

```{r cars}
library(png)
library(grid)
library(ggplot2)
library(xtable)
require(here)
require(tidyverse)
require(tidyboot)
library(apa) # for generating APA-style text to report statistical tests
library(ggpubr)
require(gridExtra)
require(papaja)
require(kableExtra)
#require(qualtRics)
require(lmerTest)
require(ggpubr)
```

@@

sum(is.na(int_long$rating))
sum(is.na(lik_long$rating))

```

@@

```{r}
#combos = adult_long %>% distinct(drop, choice, target)
distractors = c("trig prism", "trig prism", "octahedron", "sphere", "octahedron", "pyramid", "pyramid", "sphere", "sphere", "pyramid", "octahedron", "dumbbell", "dumbbell", "sphere", "pentagon", "cone", "octahedron", "dumbbell", "dumbbell", "cone")

adult_agg <- adult_long %>% group_by(drop, target, relation) %>%
  summarize(chose_target = mean(chose_target))

adult_agg$distractor = distractors
  # do we want raw counts for chose target vs. foil?
# for trial 1, 70% chose target (30% chose distractor)

child_agg <- child_long %>% group_by(drop, target, relation) %>%
  summarize(chose_target = mean(chose_target))

child_agg$distractor = distractors
```

@@

```{r}
lik_agg <- lik_long %>% mutate(rating = as.numeric(rating)) %>%
  group_by(drop, choice) %>%
  summarise(likelihood = mean(rating) - 1) # shift from 1-6 to 0-5

int_agg <- int_long %>% mutate(rating = as.numeric(rating)) %>%
  group_by(drop, choice) %>%
  summarise(interest = mean(rating) - 1) 
# also want ratings scaled 0-1?
```

## Merge ratings with adults' drop choices

```{r}
adult_agg <- adult_agg %>% left_join(lik_agg, by=c("drop"="drop", "target"="choice")) %>%
  rename(target_likelihood = likelihood) %>%
  left_join(lik_agg, by=c("drop"="drop", "distractor"="choice")) %>%
  rename(distractor_likelihood = likelihood)

adult_agg <- adult_agg %>% left_join(int_agg, by=c("drop"="drop", "target"="choice")) %>%
  rename(target_interest = interest) %>%
  left_join(int_agg, by=c("drop"="drop", "distractor"="choice")) %>%
  rename(distractor_interest = interest)

adult_agg <- adult_agg %>% 
  mutate(prop_target_likelihood = target_likelihood / (target_likelihood + distractor_likelihood),
         prop_target_interest = target_interest / (target_interest + distractor_interest))
```

## Merge ratings with children's drop choices

```{r}
child_agg <- child_agg %>% left_join(lik_agg, by=c("drop"="drop", "target"="choice")) %>%
  rename(target_likelihood = likelihood) %>%
  left_join(lik_agg, by=c("drop"="drop", "distractor"="choice")) %>%
  rename(distractor_likelihood = likelihood)

child_agg <- child_agg %>% left_join(int_agg, by=c("drop"="drop", "target"="choice")) %>%
  rename(target_interest = interest) %>%
  left_join(int_agg, by=c("drop"="drop", "distractor"="choice")) %>%
  rename(distractor_interest = interest)

child_agg <- child_agg %>% 
  mutate(prop_target_likelihood = target_likelihood / (target_likelihood + distractor_likelihood),
         prop_target_interest = target_interest / (target_interest + distractor_interest))
```

## Compare adult choice proportions vs. likelihood proportions

Regression:

```{r}
m_lik <- lm(chose_target ~ relation * prop_target_likelihood, data=adult_agg)
m_int <- lm(chose_target ~ relation * prop_target_interest, data=adult_agg)
summary(m_lik) # Rsq = .63
summary(m_int) # Rsq = .84
anova(m_lik, m_int)

m3 <- lm(chose_target ~ relation * prop_target_likelihood + relation * prop_target_interest, data=adult_agg)
summary(m3)
```

```{r}
p1 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_target_likelihood, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(method = "pearson")

p2 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_target_interest, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Interestingness") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(method = "pearson")

ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
```
